\hypertarget{1_88_84__epars_8h}{}\section{Vienna\+R\+N\+A/params/1.8.4\+\_\+epars.h File Reference}
\label{1_88_84__epars_8h}\index{Vienna\+R\+N\+A/params/1.\+8.\+4\+\_\+epars.\+h@{Vienna\+R\+N\+A/params/1.\+8.\+4\+\_\+epars.\+h}}


Free energy parameters for parameter file conversion.  




\subsection{Detailed Description}
Free energy parameters for parameter file conversion. 

This file contains the free energy parameters used in Vienna\+R\+N\+A\+Package 1.\+8.\+4. They are summarized in\+:

D.\+H.\+Mathews, J. Sabina, M. Z\+Uker, D.\+H. Turner \char`\"{}\+Expanded sequence dependence of thermodynamic parameters improves
prediction of R\+N\+A secondary structure\char`\"{} J\+MB, 288, pp 911-\/940, 1999

Enthalpies taken from\+:

A. Walter, D Turner, J Kim, M Lyttle, P M\char`\"{}uller, D Mathews, M Zuker
\char`\"{}Coaxial stckaing of helices enhances binding of oligoribonucleotides.." P\+N\+AS, 91, pp 9218-\/9222, 1994

D.\+H. Turner, N. Sugimoto, and S.\+M. Freier. \char`\"{}\+R\+N\+A Structure Prediction\char`\"{}, Ann. Rev. Biophys. Biophys. Chem. 17, 167-\/192, 1988.

John A.\+Jaeger, Douglas H.\+Turner, and Michael Zuker. \char`\"{}\+Improved predictions of secondary structures for R\+N\+A\char`\"{}, P\+N\+AS, 86, 7706-\/7710, October 1989.

L. He, R. Kierzek, J. Santa\+Lucia, A.\+E. Walter, D.\+H. Turner \char`\"{}\+Nearest-\/\+Neughbor Parameters for G\+U Mismatches....\char`\"{} Biochemistry 1991, 30 11124-\/11132

A.\+E. Peritz, R. Kierzek, N, Sugimoto, D.\+H. Turner \char`\"{}\+Thermodynamic Study of Internal Loops in Oligoribonucleotides...\char`\"{} Biochemistry 1991, 30, 6428--6435 